Mg Depleted and K Enriched Stars from LAMOST Spectral Data

### 2018-01-15 article/ms.tex
reworded much of the abstract

Stellar absorption spectra act as a fossil record of the environment of primordial conditions. Stars displaying unusual elemental abundances provide are of particular interest, as they offer the opportunity to learn about astrophysical events and objects that may no longer exist in our Galaxy. Stars with depleted Mg and enhanced K abundances present just such an opportunity. Thus far found only in two massive globular clusters NGC 2419 and NGC 2808, the primordial origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters. A satisfactory explanation for this signature has potential ramifications on theories of globular cluster formation and the long-standing problem of the underestimation of even galaxy-normal K abundances. The apparent exclusivity of this Mg-K anti-correlation to globular clusters is the focus of this survey. Here we present 113 field stars showing depleted Mg and enhanced K, though none with abundances extreme enough to be comparable to the stars identified in NGC 2419.

>>>>

Stellar absorption spectra act as a record of the primordial conditions within which the star formed. Stars displaying unusual elemental abundances provide are of particular interest; these rare stars often offer clues about astrophysical events and objects that may no longer exist in our galaxy. Stars with  depleted Mg and enhanced K abundances have thus far found only in two massive globular clusters: NGC 2419 and NGC 2808. The primordial origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters. A satisfactory explanation for this signature has potential to influence theories of globular cluster formation and shed light on the long-standing problem of the underestimation of even stars with typical galactic values of K abundances. The apparent exclusivity of this Mg-K anti-correlation to globular clusters is the focus of this survey. Here we present 113 candidate field stars (from a sample size of \LamostGiants \ giants from \lamost \ DR2) that have spectra consistent with anomalously depleted Mg and enhanced K abundances, though none with abundances comparable to the stars identified in NGC 2419.
